Sequence assembly

### 2023-05-17 episodes/sequence-assembly.Rmd
Getting students to trim all reads; working on Snps-phylogeny

>>>>

## Downloading the missing assemblies

If you haven't assembled all samples, download the finished contigs to your computer and decompress them. They will decompress in a folder called `assembly`, so one solution is to rename the assembly folder you already have to something else:

```bash
cd ~/molepi/results
mv assembly partial_assembly
wget https://github.com/lguy/course-microbial-genomics/raw/main/episodes/files/assemblies.tar.gz .
tar xvzf assemblies.tar.gz
ls assembly
```

```output
ERR026473.fasta ERR026478.fasta ERR026482.fasta ERR029207.fasta
ERR026474.fasta ERR026481.fasta ERR029206.fasta
```
